% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Professional Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}

  \experience
  {December 2024} {Senior Software Engineer}{Flomics}{Barcelona, Spain}
  {May 2020}{\begin{itemize}
    \item  Designed and maintained in-house software solutions, including:
    \begin{itemize}
    \item Flomics Stratus: a bioinformatics cloud platform for data processing and analysis.
    \item Flomics LIMS: a Laboratory Information Management System to streamline lab operations.
    \end{itemize}
    \item Established pipelines and procedures to enhance software development efficiency.
    \item Managed and optimized cloud infrastructure to ensure performance, scalability, reliability and security.
    \item Provided technical leadership and guidance to junior developers, promoting knowledge sharing, collaboration and professional growth.
  \end{itemize}}
  {Remote}{Advisor}{Typescript/WildStrawberry, Python/WildStrawberry, NestJS/CornflowerBlue, Next.js/CornflowerBlue, AWS/BlueViolet, Redis/BlueViolet, Playwright/BlueViolet, Github Actions/BlueViolet, Asana/Melon}
  
  \emptySeparator

  \experience
  {June 2024} {Senior Software Engineer}{Lyfegen}{Basel, Switzerland}
  {November 2023}{\begin{itemize}
    \item Led the improvement of code quality and functionality for Lyfegen's core product.
    \item Played a key role in transitioning to a microservices architecture.
    \item Actively contributed to the design and development of scalable performant solutions.
    \item Established and enforced coding guidelines and best practices, fostering a culture of excellence and continuous improvement within the team.
  \end{itemize}}
  {Remote}{Full-Time}{Typescript/WildStrawberry, C\#/WildStrawberry, React/CornflowerBlue, Azure Functions/CornflowerBlue, Kafka/BlueViolet, Azure/BlueViolet, PostgreSQL/BlueViolet, Neo4j/BlueViolet, Azure DevOps/Melon}

  \emptySeparator

  \experience
  {Dec 2022} {Software Engineer}{Cosuno}{Berlin, Germany}
  {May 2022}{\begin{itemize}
    \item Designed and developed features for a cloud-based platform tailored to the construction industry.
    \item Ensured a user-centric design, optimizing the interface for a clear and intuitive user experience.
    \item Conducted comprehensive testing on Back-End, Front-End, Database, and External Services components, validating all use cases to ensure high-quality releases.
  \end{itemize}}
  {Remote}{Full-Time}{Typescript/WildStrawberry, React/CornflowerBlue, NodeJS/CornflowerBlue, GraphQL/BlueViolet, Cypress/BlueViolet, Prisma/BlueViolet, Docker/BlueViolet, Notion/Melon, Jira/Melon}

  \emptySeparator

  \experience
  {April 2022} {Software Engineer}{Dunelm}{London, United Kingdom}
  {August 2021}{\begin{itemize}
    \item Automated customer success analytics processes to boost sales and retention.
    \item Streamlined workflows by developing and deploying strategic solutions.
    \item Collaborated with cross-functional teams to ensure seamless project delivery.
  \end{itemize}}
  {Remote}{Full-Time}{Typescript/WildStrawberry, React/CornflowerBlue, AWS CDK/CornflowerBlue, Microservices/BlueViolet, GitLab/BlueViolet, Datadog/BlueViolet, Prismic/BlueViolet, Jira/Melon}

\end{experiences}