% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Professional Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}

  \experience
  {December 2024} {Senior Software Engineer}{Flomics}{Barcelona, Spain}
  {May 2020}{\begin{itemize}
    \item  Designed and maintained in-house software solutions, including:
    \begin{itemize}
    \item Flomics Stratus: a bioinformatics cloud platform for data processing and analysis.
    \item Flomics LIMS: a Laboratory Information Management System to streamline lab operations.
    \end{itemize}
    \item Established pipelines and procedures to enhance software development efficiency.
    \item Managed and optimized cloud infrastructure to ensure performance, scalability and reliability.
  \end{itemize}}
  {Remote}{Advisor}{Typescript/WildStrawberry, Python/WildStrawberry, NestJS/CornflowerBlue, Next.js/CornflowerBlue, AWS/BlueViolet, Redis/BlueViolet, Playwright/BlueViolet, Github Actions/BlueViolet, Asana/Melon}
  
  \emptySeparator

  \experience
  {June 2024} {Senior Software Engineer}{Lyfegen}{Basel, Switzerland}
  {November 2023}{\begin{itemize}
    \item Enhanced code quality and functionality of Lyfegen's main product.
    \item Played a key role in transitioning to a microservices architecture.
    \item Implemented back-end microservices to improve scalability and database performance.
    \item Actively contributed to the design and development of scalable solutions.
  \end{itemize}}
  {Remote}{Full-Time}{Typescript/WildStrawberry, C\#/WildStrawberry, React/CornflowerBlue, Azure Functions/CornflowerBlue, Kafka/BlueViolet, Azure/BlueViolet, PostgreSQL/BlueViolet, Neo4j/BlueViolet, Azure DevOps/Melon}

  \emptySeparator

  \experience
  {Dec 2022} {Software Engineer}{Cosuno}{Berlin, Germany}
  {May 2022}{\begin{itemize}
    \item Designed and implemented a cloud-based solution for the construction industry.
    \item Developed planning functionalities to improve efficiency and accuracy in projects.
    \item Ensured seamless integration of new features using modern web technologies.
  \end{itemize}}
  {Remote}{Full-Time}{Typescript/WildStrawberry, React/CornflowerBlue, NodeJS/CornflowerBlue, GraphQL/BlueViolet, Cypress/BlueViolet, Prisma/BlueViolet, Docker/BlueViolet, Notion/Melon, Jira/Melon}

  \emptySeparator

  \experience
  {April 2022} {Software Engineer}{Dunelm}{London, United Kingdom}
  {August 2021}{\begin{itemize}
    \item Automated customer success analytics processes to boost sales and retention.
    \item Streamlined workflows by developing and deploying strategic solutions.
    \item Collaborated with cross-functional teams to ensure seamless project delivery.
  \end{itemize}}
  {Remote}{Full-Time}{Typescript/WildStrawberry, React/CornflowerBlue, AWS CDK/CornflowerBlue, Microservices/BlueViolet, GitLab/BlueViolet, Datadog/BlueViolet, Prismic/BlueViolet, Jira/Melon}

  \emptySeparator

  \experience
  {August 2021} {Software Engineer}{Void Software}{Leiria, Portugal}
  {September 2019}{\begin{itemize}
    \item Developed full-stack applications with a focus on security and coding best practices.
    \item Led the development of scalable and maintainable software architectures.
    \item Demonstrated expertise in frontend and backend technologies for seamless integration.
  \end{itemize}}
  {Hybrid}{Full-Time}{Typescript/WildStrawberry, Java/WildStrawberry, React/CornflowerBlue, Quarkus/CornflowerBlue, Redux/BlueViolet, Jest/BlueViolet, SCSS/BlueViolet, Jenkins/BlueViolet, SonarQube/BlueViolet, Jira/Melon}

  \emptySeparator

  \experience
  {March 2019} {Scientific Researcher}{Polytechnic of Leiria}{Leiria, Portugal}
  {October 2018}{\begin{itemize}
    \item Collaborated on the "Care4Value" project to create a digital healthcare platform.
    \item Developed a mobile application and web platform for clinical data collection.
    \item Ensured project deliverables aligned with research goals and user requirements.
  \end{itemize}}
  {Hybrid}{Full-Time}{Javascript/WildStrawberry, PHP/WildStrawberry, React Native/CornflowerBlue, Laravel/CornflowerBlue, SQLite/BlueViolet, MySQL/BlueViolet, Trello/Melon}

\end{experiences}